Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-13 paper.tex
Schemas sur_relaxation

As illustrated in Figure \ref{alternate_projections} (a-b), the Sinkhorn algorithm, that  realizes alternate Bregman projections onto the affine sets $\Ccal_1$ and $\Ccal_2$, can be very slow when $\epsilon\to 0$. The idea developped in this paper is to realize over-relaxed projections in order to accelerate the process, as displayed in Figure \ref{alternate_projections} (c)

\begin{figure}[ht!]
\begin{center}
\begin{tabular}{ccc}
%\includegraphics[width=3cm]{}&\includegraphics[width=3cm]{}&\includegraphics[width=3cm]{}\\
&TODO: mettre les figures du beamer\\
&en remplacant les $x$ par des $\gamma$\\
(a)&(b)&(c)
\end{tabular}
\caption{\label{alternate_projections} The trajectory of $\gamma^l$ given by the Sinkhorn algorithm is illustrated for decreasing values of $\epsilon$ in (a) and (b). In order to accelerate the convergence rate, over-relaxed projections are here considered (c).}
\end{center}
\end{figure}
\subsection{Over-relaxed projections}

>>>>

As illustrated in Figure \ref{alternate_projections} (a-b), the Sinkhorn algorithm, that  performs alternate Bregman projections onto the affine sets $\Ccal_1$ and $\Ccal_2$, can be very slow when $\epsilon\to 0$. The idea developped in this paper is to realize over-relaxed projections in order to accelerate the process, as displayed in Figure \ref{alternate_projections} (c)

\begin{figure}[ht!]
\begin{center}
\begin{tabular}{ccc}
\includegraphics[height=4cm]{schema_a.png}&\includegraphics[height=4cm]{schema_b.png}&\includegraphics[height=4cm]{schema_c.png}\\
(a)&(b)&(c)
\end{tabular}
\caption{\label{alternate_projections} The trajectory of $\gamma^l$ given by the Sinkhorn algorithm is illustrated for decreasing values of $\epsilon$ in (a) and (b). In order to accelerate the convergence rate, over-relaxed projections are here considered (c).}
\end{center}
\end{figure}
\subsection{Over-relaxed projections}
